\cvsection{Publications \& Presentations}

\cvevent{Working Paper}{Ports \& Adapters (Working Title)}{2026}{}
\begin{itemize}
    \item Research paper and project; forthcoming publication.
\end{itemize}

\cvevent{Workshop \& Panel}{AI for the Public Good: Methodologies and Ethics (Working Title)}{February 2026}{Massey College}
\begin{itemize}
    \item Panel of Experts facilitation; workshop facilitation; participant research.
\end{itemize}

\cvevent{Collaborative Research Project}{AI for the Public Good: Methodologies and Ethics}{2025--2026}{Massey College}
\begin{itemize}
    \item Collaborative research project on LLMs and research methods in academia; forthcoming publication.
\end{itemize}

\cvevent{Working Paper}{The Qualitative Turn in Quantitative Political Science}{December 2025}{}
\begin{itemize}
    \item Research paper; to be published.
\end{itemize}

\cvevent{Working Paper}{"New Orders of Interaction: The Sociality of Intelligent Systems and Machines That Talk Back"}{2026}{}
\begin{itemize}
    \item Major research paper; to be submitted. Draft available on request.
\end{itemize}

\cvevent{Working Paper}{Pareto-optimal Predictive Vote Probability}{2025}{Conference Paper}
\begin{itemize}
    \item Paper in-progress; to be submitted at CES 2025 Democracy Checkup.
\end{itemize}

\cvevent{Presentation}{Canadian Election Survey (CES) Hackathon}{2025}{Academic Competition}
\begin{itemize}
    \item Novel computational framework for Canadian election forecasting; demonstration.
\end{itemize}

\emph{Available upon request.}


