\cvsection{Research Experience}

\cvevent{Collaborative Researcher}{Multi-Agent Social Simulation}{2024--Present}{}
\begin{itemize}
  \item Designed multi-agent simulations across multiple domains:
  \begin{itemize}
    \item Medical differential diagnosis experiments and simulated consultation panels
    \item Political cleavages in municipal politics (Toronto bike lane expansion)
    \item Classical sociological and economic theory
  \end{itemize}
  \item Led tutorial development (transcript close-reading; prompt-engineering) aligning technical steps with sociological theory.
\end{itemize}

\cvevent{Graduate Research Fellow}{UTSC Policy Horizons Research Team}{2025--Present}{}
\begin{itemize}
    \item Designed novel multi-objective machine learning framework for American and Canadian election forecasting.
    \item Contributed to quantitative research frameworks integrating modular system architectures (Ports \& Adapters pattern).
    \item Developed LLM-based pedagogical tools and assistants for integration into complex educational systems.
    \item Applied multi-agent frameworks to model socio-political behavior and collective decision-making processes.
    \item Engaged in interdisciplinary theory construction bridging computational methods, sociological theory, and political science.
\end{itemize}

\cvevent{Independent Projects}{Antifinity \& Quantum Surplus Emergence}{2023--Present}{}
\begin{itemize}
  \item Developed theoretical and computational frameworks at the intersection of sociology, philosophy, and simulation; produced analytic write-ups and code artifacts.
\end{itemize}

\cvevent{Independent Projects}{Émile (Emergent Interactive Learner) Framework}{2023--Present}{}
\begin{itemize}
  \item Developed multi-agent orchestration platform to run local LLMs and execute dynamic agent generation informed by contextual factors.
  \item Developed open-source applications to democratize access and use of LLM technology.
  \item Developing novel approach to artificial intelligence from first principles rooted in sociological theory and phenomenology.
\end{itemize}
